### 2025-07-31 research-methods.qmd
20250731 - addition

A research question is a question that the investigator (you!) wants to know the answer to.
For example, a research question might be: "Does consumption of sports drink improve player performance?"
A hypothesis is a proposed explanation.
A prediction is "the expected result of a test that is derived, by deduction, from a hypothesis or theory" [@Eastwell2014, p. 17; archived at <https://perma.cc/8EX4-8JYN>].
Here is an example of a hypothesis and the resulting prediction:

>>>>

A research question is a question that the investigator (you!) wants to know the answer to.
For example, a research question might be: "Does consumption of sports drink improve player performance?"
A hypothesis is a proposed explanation; it specifies the causal relation between processes.
A prediction is "the expected result of a test that is derived, by deduction, from a hypothesis or theory" [@Eastwell2014, p. 17; archived at <https://perma.cc/8EX4-8JYN>].
Here is an example of a hypothesis and the resulting prediction:
